A Comparison of Neural Network Models for Water Quality Forecasting

### 2024-05-02 manuscript/manuscript.Rmd
Converging on final plots I think

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_oxygen.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive Oxygen}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_temperature.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_temperature.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive temperature}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_chla.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_chla.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive chla}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/global_loc_historical_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/date_type_global_historical_oxygen.png}
  \end{subfigure}
  \caption{Global performance on oxygen}
\end{figure}

>>>>

\begin{table}[!htbp]
    \centering
    \caption{Mean CRPS and RMSE}
    \begin{subtable}{\textwidth}
        \centering
        \caption{Dissolved Oxygen}
        \begin{tabular}{lcc}
            \toprule
            Model & Mean CRPS & Mean RMSE \\
            \midrule
            Climatology & 0.62 & 0.92 \\
            Naive Persistence & & 1.55 \\
            AutoTheta & 0.67 & 1.02 \\
            BlockRNN & 0.52 & 0.80 \\
            DLinear & 0.52 & 0.81  \\
            NBEATS & 0.51 & 0.80 \\
            NLinear & 0.52 & 0.80 \\
            \textbf{NaiveEnsemble} & \textbf{0.47} & \textbf{0.74} \\
            RNN & 0.60 & 0.92 \\
            TCN & 0.62 & 0.98 \\
            TFT & 0.52 & 0.80 \\
            Transformer & 0.51 & 0.80 \\
            \bottomrule
        \end{tabular}
    \end{subtable}
    \begin{subtable}{\textwidth}
        \centering
        \caption{Water Temperature}
        \begin{tabular}{lcc}
            \toprule
            Model & Mean CRPS & Mean RMSE \\
            \midrule
            Climatology & 1.46 & 2.19 \\
            Naive Persistence & & 6.05 \\
            AutoTheta & 1.55 & 2.35 \\
            BlockRNN & 1.45 & 2.26 \\
            DLinear & 1.35 & 2.08 \\
            NBEATS & 1.36 & 2.10 \\
            NLinear & 1.33 & 2.06 \\
            \textbf{NaiveEnsemble} & \textbf{1.18} & \textbf{1.80} \\
            RNN & 1.32 & 2.03 \\
            TCN & 1.89 & 3.02 \\
            TFT & 1.19 & 1.86 \\
            Transformer & 1.32 & 2.05 \\
            \bottomrule
        \end{tabular}
    \end{subtable}
    \begin{subtable}{\textwidth}
        \centering
        \caption{Chlorophyll-a}
        \begin{tabular}{lcc}
            \toprule
            Model & Mean CRPS & Mean RMSE \\
            \midrule
            Climatology & 4.83 & 7.50 \\
            \textbf{Naive Persistence} & & \textbf{4.86} \\
            AutoTheta &  4.20 & 6.31 \\
            \textbf{BlockRNN} & \textbf{3.14} & 5.16 \\
            DLinear & 3.47 & 5.48 \\
            NBEATS & 3.78 & 5.95 \\
            NLinear & 3.67 & 5.63 \\
            NaiveEnsemble & 3.44 & 5.50 \\
            RNN & 4.15 & 6.40 \\
            TCN & 3.72 & 5.77 \\
            TFT & 3.67 & 5.87 \\
            Transformer & 4.02 & 6.35 \\
            \bottomrule
        \end{tabular}
    \end{subtable}
    \label{tab:mean_crps_rmse}
\end{table}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend_0.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_oxygen.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive Oxygen}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend_0.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_temperature.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_temperature.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive temperature}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend_1.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_chla.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_chla.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive chla}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/forecast_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/oxygen_theta.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/chla_theta.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/oxygen_tft.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/chla_tft.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/oxygen_ensemble.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/chla_ensemble.png}
  \end{subfigure}
  \caption{Individual Forecast Examples}
\end{figure}
